Distributed Version Control Systems

### 2010-04-27 paper.tex
Sección Tagging and Branching corregida un poquito.

Centralized VCS's like Subversion makes certain copies through history called tags. 
But on Git we have more tools, one of them is that we can have an arbitrary 
description attached in the tag, in fact, you can store the whole release announcements here. 
Moreover, as with the commit, is stored the identity of who made the tag and this identity 
can be verified if we add a cryptographically PGP sign to the tag.

>>>>

Centralized VCS's like Subversion makes certain copies through history called tags. 
On Git we have more tools, with one of them you can have an arbitrary 
description attached in the tag. In fact, you can store the whole release announcements there. 
Moreover, as with the commit, the identity of who made the tag is stored and this identity 
can be securely verified if we add a cryptographically PGP sign to the tag.
